Quantifying and partitioning uncertainties in retrievals of plant traits from imaging spectroscopy data

### 2021-05-05 manuscript/manuscript.tex
Minor tweaks to manuscript

\begin{table}
\caption{\label{tab:combinations} Factorial combination of inputs}
\centering
\begin{tabular}{p{0.2\linewidth}lp{0.4\linewidth}p{0.3\linewidth}}
  \hline
  Variable & Values & Comments \\
  \hline
  Atmosphere & \emph{See Table~\ref{tab:atmospheres}} & \\
  Date & March 20, June 21, September 22, December 21 & Northern hemisphere equinoxes and solstices
  Local time (24H) & 9:30, 10:00, 10:30, 12, 15:00 & Spaced over the day, with denser sampling around typical ``A-train'' satellite overpass around 10:30AM \\
  Sensor zenith (degrees) & 0, 10, 30  & \\
  Sensor relative azimuth (degrees) & 0, 30, 60, 90, 180 & \\
  \hline
  Total grid size & \multicolumn{2}{l}{64,800} \\
  \hline
\end{tabular}
\end{table}

@@

>>>>

\begin{table}
\caption{\label{tab:combinations} Factorial combination of inputs}
\centering
\begin{tabular}{p{0.2\linewidth}lp{0.4\linewidth}p{0.3\linewidth}}
  \hline
  Variable & Values & Comments \\
  \hline
  Atmosphere & 10 different atmospheres; \emph{see Table~\ref{tab:atmospheres}} & \\
  Local time (24H) & 8:30, 9:30, 10:00, 10:30, 12, 15:00 & Spaced over the day, with denser sampling around typical ``A-train'' satellite overpass around 10:30AM \\
  Elevation (km) & 0.01, 0.5, 1, 2 & \\
  Sensor zenith (degrees) & 0, 4, 8, 12  & \\  % NOTE: David says 8 and 12
  Sensor relative azimuth (degrees) & 0, 45, 90, 180 & \\
  Sensor mean SNR & 200, 300, 400 & \\
  \hline
  Total grid size & \multicolumn{2}{l}{64,800} \\
  \hline
\end{tabular}
\end{table}

@@

Variability in top-of-atmosphere radiance simulations.

Precision of reflectance retrievals.

Variability in reflectance retrievals, by source.

Precision of trait retrievals.

Variability in trait retrievals, by source.
